---
title: "Assignment 4"
author: "Rahul Sangole"
subtitle: Fractional Factorial Design – Market Research Experiment
output:
  html_document: 
    highlight: pygments
    theme: cosmo
---

Import libraries and setup the design using `pb()`. Also, overwritting the default factor names by the `factor.names` argument in `pb()` so that the dropped "I" factor name is brought back.

```{r, message=FALSE, warning=FALSE}
library(FrF2)
library(DoE.base)
library(daewr)
library(dplyr)

design <-
    pb(
        nruns = 20,
        nfactors = 19,
        factor.names = LETTERS[1:19],
        randomize = FALSE
    )

y <-
    c(
        1.04,
        0.76,
        0.84,
        2.68,
        2.08,
        1.20,
        1.22,
        1.36,
        1.14,
        0.60,
        2.16,
        0.78,
        0.80,
        0.98,
        0.74,
        1.98,
        1.72,
        0.86,
        0.94,
        2.08
    )
design <- add.response(design , y)

design
```

### 1. Verify that in this design each main effect is aliased with all 2-factor interactions except those that involve that main effect

I think this can be done visually using the `colormap()` function. Though, with the large number of factors and their 2-level interactions, it becomes very difficult to discern visually. 

First, we can look at the colormap for this PB-20 design for just the first 5 factors. We can see:

* Factor A is partially correlated with BD BE etc
* Factor B is partially correlated with AD AE CE etc
* Factor C is partially correlated with BE etc
...

Thus, each main effect is aliased with 2 factor interactions except those 2-factor interactions which contain the main effect.

```{r}
colormap(design = design[,1:5],mod = 2)
```
The colormap for the entire 20-factor design is as follows. Visually very hard to tell what's going on, but upon closer inspection, it follows the pattern above.
```{r}
colormap(design = design,mod = 2)
```

### 2. Verify that the five largest main effects are S, G, R, I, and J.

This can be done in two ways:

1. Look at the top 5 absolute values of the coefficients of a linear model:

```{r}
mod1 <- lm(y ~ (.) ^ 2, data = design)
sort(abs(coef(mod1)),decreasing = T)[2:6]
```

2. Visually, we can plot a half-normal plot and arrive at the same conclusion:
```{r}
cfs <- coef(mod1)[2:20] 
names <- names(cfs) 
halfnorm(cfs, names, alpha = .25, refline = FALSE) 
```

### 4. Fit a full factorial model involving all 3 of these factors and the interactions. Show that S, G, and the SG interaction are significant.

First, select the 3 factors S, G, R and the response y.

```{r}
df <- tbl_df(design) %>% 
    select(S,G,R,y)
print(df)
```

The first three columns contain a full factorial design in 3 factors, with a few of the runs repeated.

This can be confirmed using this code:

```{r}
df %>% select(-y) %>% unique %>% arrange(S,G,R)
```

Now, we fit a full factorial model to `df` including all 2 level interactions:

```{r}
df.lm <- lm(y~(.)^2,df)
summary(df.lm)
```
S and G are highly significant (p<1e-3), while S-G interaction is significant at the 0.05 level (p=0.35<0.05).

We can also see that the main effect R is not significant (p=0.36>0.05).